PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-19 qfenv_paper/qf_environment.tex
Edits on QFcalc and QFevol

With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}). More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EVOLUTION OF THE QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: {\it dex}$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments. As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading (darker with lower redshift) and the uncertainty is represented by the width. We use the standard jackknife technique, following the same steps as the SMF uncertainty in Section \ref{sec:smfcalc}, in order to calculate the uncertainty for the quiescent fraction.

@@

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\cite{hopkins06a}). %Maybe Stacey et al. 2014 is relevant here?

@@

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements for analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with previous SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lower mass limit ($\rm{log} \; \mathcal{M} \sim 10.2$).

At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}. \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment. Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \cite{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.

For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment. The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.

Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR. For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$. And for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$. Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin ($0.1< z < 0.4$) are generally consistent with our $f_{\rm{Q}}$ at high and low density environments. In their higher redshift bin ($0.4 < z < 0.7$), even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.

We previously addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases. This general trend is in good agreement with\cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{red}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$. However, our $f_{\rm{Q}}$ redshift evolution disagrees with \cite{Kovac:2014aa}, which presents a general decrease in $f_{\rm{red}}$ over cosmic time for low environment.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} \label{eq:qffit}
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{\mathcal{M}_{\rm{fid}}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). $\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies. We primarily focus on $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (blue) and high (red) density environments for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill).

@@

Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}. Galaxy populations in higher density environments at $z < 1.0$ have higher quenched fractions. As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).

For $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, keeping the slope the same. Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the total evolution for either environments.

On the other hand, \cite{Iovino:2010aa} finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$,  for both group and isolated galaxies. In fact for their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$), they find no evolution for both environments within $z \sim 0.3 - 0.8$. Furthermore, \cite{Iovino:2010aa} also finds that the difference in $f_{\rm{blue}}$ evolution between group and isolated galaxies ($f_{\rm{blue}, \rm{isolated}}(z) - f_{\rm{blue}, \rm{group}}(z))$ is much greater at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find no difference. So in their highest mass bin, $f_{\rm{blue}}$ remains constant at $\sim 0.1$ within $z \sim 0.3 - 0.8$ for both group and isolated galaxy populations. As noted earlier, changing the fiducial mass in our analysis does not significantly alter the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ between the low and high density environments.

The zCOSMOS results find a clear mass dependence in the $f_{\rm{blue}}$ evolution; however, the consistency in evolutionary trends when the fiducial mass is change reveal that our $f_{\rm{Q}}$ evolution exhibits little mass dependence. Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g. $\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.

Finally, from Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases. This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier. More importantly, we quantify the total evolution of $f_{\rm{Q}}$ for both low and high density environments through $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.1) - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.7)$ for both environments. Remarkably, $f_{\rm{Q}}$ evolves by the same amount for both environments. In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show little environment dependence. This disagrees with the $f_{\rm{blue}}$ results from \cite{Iovino:2010aa}, which show a clear distinction between group and isolated galaxies. In \cite{Iovino:2010aa}, $f_{\rm{blue}}$ for isolated galaxies decrease much faster than $f_{\rm{blue}}$ for group galaxies. At $\mathcal{M} \sim 10.5$, \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ for isolated galaxy decreases by 0.3 from $z \sim 0.6$ to 0.3, while for $f_{\rm{blue}}$ for group galaxies only decrease by 0.1 in the same redshift limit, showing a clear dependence in environment. Considering that fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, we consider more stringent classification of high density environments extending the cut-off to $n_{\rm{env}} > 6, 9$. While a more stringent classification increases the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ overall as well as the uncertainties, it does not reveal reveal any significant environment dependence in the $f_{\rm{Q}}$ evolution. Therefore, the potential contamination in our environment measurements cannot explain the lack of environment dependence in the $f_{\rm{Q}}$ evolution.

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) from SDSS. These $f_{\rm{red}}$ values are calculated from the best-fit parameterizations presented in the respective works. High density environment is represented in red and low density environment is represented in blue. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates. Furthermore, we also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure}

>>>>

With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}). More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EVOLUTION OF THE QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: {\it dex}$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right panel) and low (left panel) density environments. As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading (darker with lower redshift) and the uncertainty is represented by the width. For the uncertainty in the quiescent fraction, we use the standard jackknife technique, following the same steps as the SMF uncertainty in Section \ref{sec:smfcalc}.

@@

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments, a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\cite{hopkins06a}). %Maybe Stacey et al. 2014 is relevant here?

@@

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements with analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with previous SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lower mass limit ($\rm{log} \; \mathcal{M} \sim 10.2$).

At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}. \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although in these comparisons, the different environment measurements make direct comparisons unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$ in \cite{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment. Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \cite{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.

For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which covers a similar redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment. The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.

Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR. For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$. While for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$. Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we naively account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are generally consistent with our $f_{\rm{Q}}$ at high and low density environments. However, in their higher redshift bin even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.

We previously addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases. This general trend is in good agreement with \cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{blue}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$. However, in contrast to our $f_{\rm{Q}}$ redshift evolution, \cite{Kovac:2014aa} presents a notable decrease in $f_{\rm{red}}$ over cosmic time for low environment. Even for their galaxies in high density environments, \cite{Kovac:2014aa} finds no significant increase in $f_{\rm{red}}$ with cosmic time.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} \label{eq:qffit}
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{\mathcal{M}_{\rm{fid}}} \right)+b,
\end{equation}
where $a$ and $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}) and $\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies. We primarily focus on $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts.

In Figure \ref{fig:qffit} we present the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ at low (blue) and high (red) density environments for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill). Then in Figure \ref{fig:qffit_comp} we explore more stringent environment cut-offs for the high density environment (specified in the top right legend and represented by shading). In addition, we plot best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond). From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the difference between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$).

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) from SDSS. These $f_{\rm{red}}$ values are calculated from the best-fit parameterizations presented in the respective works. High density environment is represented in red and low density environment is represented in blue. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates. We also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure}

Both Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} illustrate that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa} and suggests that galaxy populations in higher density environments at $z < 1.0$ have higher quenched fractions. As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).

In Figure \ref{fig:qffit}, for $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, keeping the slope of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution the same. Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the total evolution for either environments.

The similarity of the evolutionary trends at $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ and $10^{11} \: \mathcal{M}_{\odot}$ conflicts with \cite{Iovino:2010aa} who find contrasting $f_{\rm{Q}}$ evolutions at $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ and $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$,  for both group and isolated galaxies. In fact at their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} find no evolution for both environments: $f_{\rm{blue}}$ remains constant at $\sim 0.1$ within $z = 0.3 - 0.8$ for both group and isolated galaxy populations. Meanwhile in their mass bin most comparable to our $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$, they present an evolution of $\Delta f_{\rm{red}} \sim 0.1$ over $z = 0.5$ to $0.25$ for group galaxies and $\Delta f_{\rm{red}} \sim 0.3$ over $z = 0.55$ to $0.3$. Furthermore, while we find that the $f_{\rm{Q}}(z)_{\rm{high}} - f_{\rm{Q}}(z)_{\rm{low}}$ remains relatively constant at $\sim 0.1$ over the redshift range for both fiducial masses, \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z)_{ \rm{isolated}} - f_{\rm{blue}}(z)_{\rm{group}}$ is much more significant at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find no difference.

zCOSMOS results find a clear mass dependence in the $f_{\rm{blue}}$ evolution; however, the consistency in evolutionary trends when the fiducial mass is changed reveal that our $f_{\rm{Q}}$ evolution exhibits little mass dependence. Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g. $\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.

Another trend we observe in both Figure \ref{fig:qffit} Figure \ref{fig:qffit_comp}, is that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases. This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier. More importantly, by fitting our $f_{\rm{Q}}$ evolution and obtaining the value at the fiducial mass, we are able to quantify the total evolution of $f_{\rm{Q}}$ for both low and high density environments through $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.1) - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.7)$ for both environments. In Figure \ref{fig:qffit}, we find that $f_{\rm{Q}}$ evolves by a similar amount for both environments.

Considering that fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, in Figure \ref{fig:qffit_comp}, we consider more stringent classification of high density environments extending the cut-off to $n_{\rm{env}} > 6, 9$. A more stringent classification significantly increases the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ overall. The decrease in sample size that accompanies a purer high environment sample also increase the uncertainties. More importantly, a purer high environment classification reveals a more significant environment dependence of the $f_{\rm{Q}}$ evolution. With a purer the high environment classification, we find a steeper slope in the $f_{\rm{Q}}$ and a greater total $f_{\rm{Q}}$ evolution. From $ z \sim 0.7$, for the low density environment ($n_{\rm{env}} < 0.5$) $f_{\rm{Q}}$ increases by roughly $0.1$. At the highest environments, $f_{\rm{Q}}$ increases by roughly $0.25$. Therefore, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show moderate environment dependence.

An environment dependence of the $f_{\rm{Q}}$ evolution is also observed in \cite{Iovino:2010aa} - also plotted in Figure \ref{fig:qffit_comp}. However, in addition to a much more pronounced distinction between the group and isolated $f_{\rm{Q}}$ evolution, they find the opposite environment dependence. Unlike our results, which find a greater $f_{\rm{Q}}$ evolution at higher density environments, \cite{Iovino:2010aa} finds a much greater evolution for isolated galaxies.
